\documentclass[a4paper, landscape]{article}

\usepackage[landscape]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{amssymb}
\usepackage{pifont}

\begin{document}

\begin{longtable}{p{3cm}p{5cm}p{5cm}p{5cm}}
	\toprule
	& \textbf{Language Models} & \textbf{Link Counts} & \textbf{Surface Counts} \\

	\midrule
	\textbf{Disambiguation}
		& \emph{\checkmark Ignore.} Disambiguation sites are no entities, i.e.\ we never want to link to them so a language model is not necessary.
		& \emph{\checkmark Ignore.} If two things are named similar, they do not necessarily have a semantic connection, e.g.\ "Angela Merkel" vs. "Merkel, Texas". \emph{Idea:} Redirect links to disambiguation pages to the disambiguated pages.
		& \emph{\checkmark Extract.} Could contain useful mentions, especially because usually a different link text is used for each entity.  \\
	\textbf{Redirects}
		& \emph{\checkmark Ignore.} Makes no sense to create a language model for a redirect (text is empty except \mbox{\#REDIRECT} call).
		& \emph{\checkmark Extract.} To take care of pages wrongly linking to the redirecting page. \emph{Idea:} Resolve redirects to skip the redirecting page.
		& \emph{\checkmark Extract.} Usually contain no useful mentions, but parse nevertheless. \\
	\textbf{Lists}
		& \emph{\checkmark Ignore.} Lists are no entities (or are they?).
		& \emph{\checkmark Extract.} Is this useful?
		& \emph{\checkmark Extract.} Can contain useful mentions.

	\\\bottomrule
\end{longtable}

\end{document}
